General Relativistic Ray Tracing for Neutrinos

### 2016-08-22 paper.tex
Add notes on error in Boltzmann Equation

The neutrino distribution function, $f(p_\beta; x^\alpha)$ is an invariant
quantity counting the number of neutrinos in a given momentum volume centered on
$p_\beta$ and spatial volume centered on $x^\alpha$.
The neutrino momentum is written
\begin{equation}
  \label{eqn:def_momentum}
  p_\beta = \varepsilon (u_\beta + \ell_\beta),
\end{equation}
with $u^\beta$ a general observer's velocity,
$\varepsilon$ the energy measured by that observer,
and $\ell_\beta$ the direction vector subject to the constraints
$u^\alpha \ell_\alpha = 0$ and
$\ell^\alpha \ell_\alpha=1$.
Because $\ell$ is normalized and perpendicular to the observer's velocity,
it has two degrees of freedom, which we can make explicit by defining its
spatial components with respect to spherical polar angles
\begin{equation}
  \label{eq:def_direction}
  \ell_i :=
  (\sin\upsilon_1\cos\upsilon_2,\sin\upsilon_1\sin\upsilon_2,\cos\upsilon_1).
\end{equation}

Neutrino radiation obeys the relativistic Boltzmann equation
\todo{integral isn't explicitly covariant}
\begin{equation}
  \label{eqn:boltzmann}
  p^\beta \nabla_\beta f = \mathscr{E} - \mathscr{K} f
  + \mathscr{K}_s \oint d\ell' \phi(\ell_\alpha,\ell_\beta') f,
\end{equation}
where $\nabla_\beta$ denotes a covariant derivative. We have introduced
$\mathscr{E}$, the invariant emissivity,
$\mathscr{K}\equiv\mathscr{K}_a+\mathscr{K}_s$, the invariant total opacity
comprised of absorption and scattering opacities, and
$\phi(\ell_\alpha,\ell_\beta')$, the elastic scattering kernel, representing the
likelihood of scattering from the direction $\ell_\beta'$ to the direction
$\ell_\alpha$, subject to the normalization
\todo{confirm this}
\begin{equation}
  \oint d\ell' \phi(\ell_\alpha,\ell_\beta') = 1.
  \nonumber
\end{equation}

>>>>

The neutrino distribution function, $f(p_\beta; x^\alpha)$ is an invariant
quantity counting the number of neutrinos in a given momentum volume centered on
$p_\beta$ and spatial volume centered on $x^\alpha$.
The neutrino momentum is written
\begin{equation}
  \label{eqn:def_momentum}
  p_\beta = \varepsilon (u_\beta + \ell_\beta),
\end{equation}
with $u^\beta$ a general observer's velocity,
$\varepsilon=-p_\mu u^\mu$ the energy measured by that observer,
and $\ell_\beta$ the direction vector subject to the constraints
$u^\alpha \ell_\alpha = 0$ and
$\ell^\alpha \ell_\alpha=1$.
Because $\ell$ is normalized and perpendicular to the observer's velocity,
it has two degrees of freedom, which we can make explicit by defining its
spatial components with respect to spherical polar angles
\begin{equation}
  \label{eq:def_direction}
  \ell_i :=
  (\sin\upsilon_1\cos\upsilon_2,\sin\upsilon_1\sin\upsilon_2,\cos\upsilon_1).
\end{equation}

Neutrino radiation obeys the relativistic Boltzmann equation
\todo{integral isn't explicitly covariant}
\todo{correct this to differentiate in phase space}
\begin{equation}
  \label{eqn:boltzmann}
  p^\beta \nabla_\beta f = \mathscr{E} - \mathscr{K} f
  + \mathscr{K}_s \oint d\ell' \phi(\ell_\alpha,\ell_\beta') f,
\end{equation}
where $\nabla_\beta$ denotes a covariant derivative. We have introduced
$\mathscr{E}$, the invariant emissivity,
$\mathscr{K}\equiv\mathscr{K}_a+\mathscr{K}_s$, the invariant total opacity
comprised of absorption and scattering opacities, and
$\phi(\ell_\alpha,\ell_\beta')$, the elastic scattering kernel, representing the
likelihood of scattering from the direction $\ell_\beta'$ to the direction
$\ell_\alpha$, subject to the normalization
\todo{confirm this}
\begin{equation}
  \oint d\ell' \phi(\ell_\alpha,\ell_\beta') = 1.
  \nonumber
\end{equation}
